An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/concl.tex
config: concl

In this paper, we introduce \app, a highly modular framework 
that allows verification of configuration files, 
even without a language model of the file.
New verification properties require only a small amount of code 
and are not language specific, 
all indicating that \app could be widely adopted by system administrators.
Such a verification tool that scales in both performance and expressivity 
can revolutionize configuration file checking, 
reducing the cost of system maintenance and failure dramatically.

>>>>

In this paper, we introduce \app, a highly modular framework 
that allows automatic verification of configuration files.
\app employs translator to parse a sample configuration dataset
into well-structured and typed intermediate representation,
and then uses a learner module to derive rules, 
thus building a language model.
For a given configuration file we want to verify,
\app uses the generated language model to check
whether any rule is violated.
We evaluate \app using a real-world dataset~\cite{configdataset}
which contains 261 incorrect MySQL configuration files.
Our experimental result shows \app is able to
correctly detect errors in 217 files (\ie, 83\% accuracy).
